The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-13 paper/ms.tex
more on bias

In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. From the HR diagram, we identify 64 of these objects as evolved systems, and the remaining~38 lie on the main sequence. One of the main sequence objects, BD+43~3068 is a G0 dwarf with a $G$ magnitude of 8.267944 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a Solar analogue: it is possible that it was previously misidentified as a giant. Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.

>>>>

In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the remainder of the \kepler sample.

From the HR diagram, we identify 64 of these objects as evolved systems, and the remaining~38 lie on the main sequence. One of the main sequence objects, BD+43~3068 is a G0 dwarf with a $G$ magnitude of 8.267944 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a Solar analogue: it is possible that it was previously misidentified as a giant. Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.
